---
title: "03-lab3"
format: html
editor: visual
---

Libraries

```{r}
library("IRanges")
library("GenomicRanges")
library("Rsamtools")
library("GenomicAlignments")
library("Gviz")
library(readr)
library(Biostrings)
```

Question 1

```{r}
flye_output <- read_log(file = "~/outputs/flye_output/flye.log")
flye_results <- paste(flye_output$X1[13369: 13363], flye_output$X2[13369: 13363], sep = " ")
table <- data.frame(flye_results)
table
```

(Will need to find a way to read length of file instead of manually inputting length values) Considering the total length of the sequence is 10,226,846, and the S. cerividae genome is approximately 12Mb, I would not expect all of the genome to be present. In addition, the mean coverage of 6 is incredibly poor by modern standards.

Question 2 The Busco file reports a completeness percentage of 15.6%, which is quite garbage. Alongside the coverage of from the flye report, I assume that the completeness is also quite trash since it only has 6 bases on average to compare to. The N50 Busco reports is 28,271, which is comparable to the 28,892 flye reports The total assembly length is 10,063,190, which is somewhat comparable to the 10,226,846 flye reports.

Question 3 quast reports a genome fraction of 1.625 (162.5%), which is a very different number compared to the 15.6% reported by Busco. The duplication ratio is 1.027. It had 1 misassembly, with the length of this contig being 18,028.

Question 4

```{r}
library(Biostrings)
source <- "~/data/S288C_UCSC.fna"
fna <- readDNAStringSet(source)
frame <- data.frame(fna)
chrI <- paste(">chrI", frame[1, ], sep = " ")
fileName <- "~/outputs/R64_chr1.fna"
file.create(fileName)
writeLines(chrI, fileName)
```

Question 5
In total there are 4 contigs mapped. According to the ranges, the contigs are only around 6,000 base pairs in length in total, thus this barely covers any size. In contrast, the QUAST report reports 100x more contigs and most contigs are longer than the sum of all contigs reported by the BAM file. 

```{r}
bam_file <- "~/outputs/alignment.sorted.bam"
bam <- BamFile(bam_file)
alns <- readGAlignments(bam)
gr_alns <- granges(alns)

aln_track <- AnnotationTrack(gr_alns, name = "Contigs", genome = "sacCer3", chromosome = "chrI")
axis_track <- GenomeAxisTrack()

# Plot
plotTracks(list(axis_track, aln_track),
           from = min(start(gr_alns)),
           to = max(end(gr_alns)),
           main = "Contig Alignments to Chromosome 1")
```

Question 6
Got contig sorting function from google AI but for some reason R documentation is not responding, so I assume it says the same there
```{r, echo = false}
consensus <- "~/outputs/medaka_round2/consensus.fasta"
contigs <- readDNAStringSet(consensus)
sorted_contigs <- contigs[order(width(contigs), decreasing = TRUE)]
frame <- data.frame(sorted_contigs)
longest_contig <- paste(">longest_contig", frame[1, ], sep = "\n")
fileName <- "~/outputs/longest_contig.fasta"
file.create(fileName)
writeLines(longest_contig, fileName)
```

Question 7
Convert sam to bam. Sort and index created bam
```{terminal}
samtools view -bS ~/outputs/cds_aln.sam > ~/outputs/cds_aln.bam
samtools sort ~/outputs/cds_aln.bam -o ~/outputs/cds_aln.sorted.bam
samtools index ~/outputs/cds_aln.sorted.bam
```

Question 8
Turn bam into something readable by Gviz
```{r}
bam_file <- "~/outputs/cds_aln.sorted.bam"

bam <- BamFile(bam_file)
alns <- readGAlignments(bam)
gr_alns <- granges(alns)

options(ucscChromosomeNames=FALSE)
aln_track <- AnnotationTrack(gr_alns, name = "Contigs", genome = "sacCer3", chromosome = "chrI")
axis_track <- GenomeAxisTrack()

# Plot
plotTracks(list(axis_track, aln_track),
           from = min(start(gr_alns)),
           to = max(end(gr_alns)),
           main = "Contig Alignments to Chromosome 1")

options(ucscChromosomeNames=FALSE)
```
